Market Expectations and Mangerial Turnover

### 2024-02-23 paper.qmd
some local changes in linux machine

The subscript $l[i]$ allows coefficient variation across groups. We investigate hierarchies across season, country and country-tier. Hierarchical priors on $\alpha,\beta$ parameters share data to obtain better estimates, even for new leagues or clubs.

@@

>>>>

The $t$ is the time to hazard in games in charges. The subscript $l[i]$ allows coefficient variation across groups. We investigate hierarchies across season, country and country-tier. Hierarchical priors on $\alpha,\beta$ parameters share data to obtain better estimates, even for new leagues or clubs.

@@

```{r}
logit |> 
  ungroup() |>
  select(cty_factor,.iteration,.chain,conditional_mean_CumRS,conditional_mean_Pcts_of_Possible) |>
  pivot_longer(!cty_factor&!.iteration&!.chain,names_to = "conditional_mean",values_to = "draws") |>  
  group_by(cty_factor,conditional_mean) |>
  mutate(global_mean=mean(draws)) |>
  ggplot(aes(x = reorder(cty_factor,global_mean),
             y=draws, 
             fill =conditional_mean)) +
  stat_slab() +
  labs(x="",
       title="Overall effect on probability of poaching",
       subtitle="Posterior probability distribution",
       y="Overall Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/logit_by_cty.png",width = 12,height = 8)
